A state space model for discovering the trajectory dynamics of replay

### 2020-03-04 Article.tex
Update on Overleaf.

Just for kicks here's a citation \cite{Gustafsson2016}. And a reference to a supplement \cref{note:Note1}. And \nameref{note:Note1}.
\Blindtext

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure2.pdf}
\caption{Simulated data used to fit the encoding model. \textbf{a.} Place fields for each cell are simulated as a Gaussian with a maximum firing rate of 15 spikes / s. \textbf{b.} Position is simulated as a sinusoid to mimic an animal moving back and forth on a linear track. Each cell is simulated as a inhomogeneous Poisson process with a rate that depends on position according to its place field in a.}
\label{fig:computerNo}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure3.pdf}
\caption{Model can classify each category of trajectory dynamic (and combinations of dynamics) on simulated data. Each panel has three plots that show (from top to bottom) the simulated cell population activity, the probability of the three trajectory dynamics at each time, and the decoded posterior probability of position at each time. \textbf{a.} Continuous. \textbf{b.} Hover. \textbf{c.} Fragmented. \textbf{d.} Hover-Continuous-Hover. \textbf{e.} Fragmented-Continuous-Fragmented. \textbf{f.} Fragmented-Hover-Fragmented.}
\label{fig:computerNo}
\end{figure}

@@

\section*{References}
\bibliography{zHenriquesLab-Mendeley}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Supplemental_Figure3.pdf}
\caption{Increasing the probability of transitioning within category.}
\label{fig:Supplemental Figure 3}
\end{figure*}

>>>>

Just for kicks here's a citation \cite{DavidsonHippocampalReplayExtended2009}. And a reference to a supplement \cref{note:Note1}. And \nameref{note:Note1}.
\Blindtext

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{figures/Figure1/Figure1_v3.pdf}
\caption{Placeholder image of Iris with a long example caption to show justification setting.}
\label{fig:computerNo}
\end{figure*}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure2/Figure2_v3.pdf}
\caption{Model can classify each category of trajectory dynamic (and combinations of dynamics) on simulated data. Each panel has three plots that show (from top to bottom) the simulated cell population activity, the probability of the three trajectory dynamics at each time, and the decoded posterior probability of position at each time. \textbf{a.} Continuous. \textbf{b.} Hover. \textbf{c.} Fragmented. \textbf{d.} Hover-Continuous-Hover. \textbf{e.} Fragmented-Continuous-Fragmented. \textbf{f.} Fragmented-Hover-Fragmented.}
\label{fig:computerNo}
\end{figure*}

@@

\section*{References}
\bibliography{refs}

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure1-supplemental1/Figure1_v1_supplemental1.pdf}
\caption{Increasing the probability of transitioning within category.}
\label{fig:Supplemental Figure 3}
\end{figure*}
